A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-08-22 old_main.tex

\begin{figure*}[h]
    \centering
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
        \caption{}
        \label{fig:time}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
        \caption{}
        \label{fig:power}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
        \caption{}
        \label{fig:cost}
    \end{subfigure}
    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets \cm{ for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot. Each color is a different device and the datasets are displayed along the first axis. Outliers are denoted with a white dot.}
    For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
\end{figure*}

@@

\begin{table*}
\centering
\caption{Comparison of AFT Models on the combined dataset. \cm{\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller one being preferred. Concordance is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model. \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model. These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}}
\label{tab:combined}
\begin{tabular}{lrrrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{AFT Models}
\label{res:aft}

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
        \caption{ }
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
        \caption{}
    \end{subfigure}
    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red). The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
    \label{fig:qq}
\end{figure*}
\begin{figure}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    % \begin{subfigure}{.5\linewidth}
        \centering
        \includegraphics[width=.5\textwidth]{plots/combined/weibull_aft.pdf}
        \caption{Coefficients of the Covariates for the Weibull AFT model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
        \label{fig:aft}
    % \end{subfigure}
    % \begin{subfigure}[b]{.45\linewidth}
    %     \centering
    %     \includegraphics[width=\linewidth]{plots/combined/weibull_device_num_partial_effect.pdf}
    %     \caption{\cm{The partial effect GPU on survival time. After accounting for GPU bandwidth (see Table~\ref{tab:hardware}) and the covariate effects of the hardware and and inference time, we se ethat Graphic}}
    %     \label{fig:partial_effect}
    % \end{subfigure}
    % \caption{Weibull AFT Model.}
\end{figure}

>>>>

\begin{figure*}[h]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
        \caption{}
        \label{fig:time}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
        \caption{}
        \label{fig:power}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
        \caption{}
        \label{fig:cost}
    \end{subfigure}
    \caption{This depicts the training, inference, and attack times (a), power (b), and cost (c), for all hardware and datasets \cm{ for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot. Each color is a different device and the datasets are displayed along the first axis. Outliers are denoted with a white dot.}
    For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
\end{figure*}

@@

\begin{table*}
\centering
\caption{Comparison of AFT Models on the combined dataset. \cm{\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller one being preferred. Concordance is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model. \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model. These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}}
\label{tab:combined}
\begin{tabular}{lrrrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}
\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
        \caption{ }
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
        \caption{}
    \end{subfigure}
    \caption{\cm{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red). The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} * N $.}}
    \label{fig:qq}
\end{figure*}
\subsection{AFT Models}
\label{res:aft}

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{plots/combined/weibull_aft.pdf}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{plots/combined/log_normal_aft.pdf}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{plots/combined/log_logistic_aft.pdf}
    \end{subfigure}
    \caption{Coefficients of the Covariates for the Weibull AFT model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
    \label{fig:aft}
\end{figure*}
